---
title: "Mission Impossible 2"
output: html_document
author: ChabertBayerJacques
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import via a csv

Import the csv file called "mi2DataAll".

```{r}
library(readr)
gdp <- read_csv("mi2DataAll.csv")
```

# Delete the column

Delete the column "X1".

```{r}
 gdp$X1 <- NULL
gdp

```

# Remove missing values

Remove all missing values from the dataframe "gdp".

```{r}
gdp2 <- tidyr::drop_na(gdp)
gdp2


```

# Gather the data

You need to gather (modify from wide to long) the dataframe "gdp2" to get three column: "country", "year", "gdp".

```{r}
library(tidyr)
gdp3 <- tidyr::gather(gdp2, "year", "gdp", 2:59)

```

# Filter the data

Filter the data to only keep the following countries: "united states", "canada", "japan", "belgique", "FRA".

```{r}
library(dplyr)
gdp4 <- filter(gdp3, country=="united states" | country=="canada" | country=="japan" | country=="belgique" | country=="FRA")

```

# Import via a gsheet 

Import the data containing the longitute and latitude from this gsheet : <https://docs.google.com/spreadsheets/d/1VUxLOL2GH2ULrZ-lqQUa5IPKeSH-4dy_hTevZUyqbv4/edit#gid=0>

```{r}
library(gsheet)
locations <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1VUxLOL2GH2ULrZ-lqQUa5IPKeSH-4dy_hTevZUyqbv4/edit#gid=0")
```

# Combining tables

Join the data frame "locations" to the data frame "gdp4". Before combining the data frames, make sure that all countries and columns have the same names!

```{r}
#renaming countries
gdp4$country <- gsub ("FRA", "France", gdp4$country)
gdp4$country <- gsub ("Belgique", "Belgium", gdp4$country)
```


```{r}
# Rename "Pays"
library(dplyr)
locations <- rename(locations, country=Pays)
```


```{r}
gdp5 <- left_join(gdp4, locations, by = "country")
```

# Delete a column

Delete the column "Continent".

```{r}
gdp5$Continent<-NULL
gdp5

```

















